Analysis of the included studies

### 2023-06-16 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Uncommented old analyses

<!-- ## Diseases studied per collab type -->

<!-- ```{r echo=FALSE} -->
<!-- #count the number of unique diseases studied -->
<!-- disease_studied_by_collab_type <- compact_data_with_citation_keys_no_fmd %>%  -->
<!--   separate_rows(disease,  sep = ' ') %>%  -->
<!--   distinct(title, disease, .keep_all = TRUE) %>%  -->
<!--   count(collab_type, disease, sort = TRUE) %>% -->
<!--   pivot_wider(names_from = collab_type, values_from = n) %>%  -->
<!--   replace_na(list(purely_academic = 0, mixed = 0)) %>%  -->
<!--   adorn_totals(where = c('row', 'col')) %>%  -->
<!--   adorn_percentages(... = c('purely_academic', 'mixed')) %>%  -->
<!--   adorn_pct_formatting(... = c('purely_academic', 'mixed')) %>%  -->
<!--   adorn_ns(... = c('purely_academic', 'mixed')) %>%  -->
<!--   mutate(disease = str_to_sentence(str_replace(disease, '_', ' '))) %>%  -->
<!--   arrange(desc(Total)) -->

<!-- knitr::kable(disease_studied_by_collab_type, caption = 'Number of studies per disease and collaboration type', format = "latex", booktabs = TRUE) %>%  -->
<!--         kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position')) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #tally the diseases by collaboration type -->
<!-- disease_by_collab_type_long <- compact_data_with_citation_keys_no_fmd %>%  -->
<!--   separate_rows(disease,  sep = ' ') %>%  -->
<!--   count(collab_type, disease, sort = TRUE)  -->

<!-- disease_by_collab_type_plot <- ggplot(disease_by_collab_type_long) +  -->
<!--   geom_bar(aes(x = reorder(disease, n),  -->
<!--                y = n,  -->
<!--                fill = collab_type -->
<!--                ),  -->
<!--            color = 'black', -->
<!--            stat = 'identity', -->
<!--            position = position_fill(reverse = TRUE) -->
<!--            ) +  -->
<!--   labs(x = '**Disease**', y = '**Number of studies**') +  -->
<!--   coord_flip() + -->
<!--   md_theme_minimal(base_size = 12) -->

<!-- print(disease_by_collab_type_plot) -->
<!-- ``` -->

@@

<!-- ### Parametrization methods -->

<!-- ```{r} -->
<!-- #wide data for table -->
<!-- model_parametrization_wide <- compact_data_with_citation_keys_no_fmd %>%  -->
<!--   count(collab_type, parametrization, sort = TRUE) %>%  -->
<!--   pivot_wider(names_from = parametrization, values_from = n) %>%  -->
<!--   adorn_totals(where = c('row', 'col')) %>%  -->
<!--   adorn_percentages(... = -c('Total', 'collab_type')) %>%  -->
<!--   adorn_pct_formatting(... = -c('Total', 'collab_type')) %>%  -->
<!--   adorn_ns(... = -c('Total', 'collab_type'))  -->

<!-- #table -->
<!-- knitr::kable(model_parametrization_wide, caption = 'How model parameters are obtained',  -->
<!--              format = "latex", booktabs = TRUE) %>%  -->
<!--         kableExtra::kable_styling(latex_options = c('striped', 'scale_down', 'HOLD_position')) -->
<!-- ``` -->

<!-- ```{r eval=FALSE} -->
<!-- #long data for plotting -->
<!-- model_parametrization_long <- compact_data_with_citation_keys_no_fmd %>%  -->
<!--   group_by(collab_type) %>%  -->
<!--   count(parametrization, sort = TRUE) -->

<!-- #plotting -->
<!-- ggplot(data = model_parametrization_long,  -->
<!--        aes(fill = collab_type,  -->
<!--            area = n,  -->
<!--            label = parametrization, -->
<!--            subgroup = parametrization -->
<!--            ) -->
<!--        ) +  -->
<!--   geom_treemap() + -->
<!--   geom_treemap_text(colour = "white", -->
<!--                     place = "centre", -->
<!--                     size = 15, -->
<!--                     grow = TRUE -->
<!--                     ) + -->
<!--   md_theme_minimal(base_size = 12)  -->

<!-- ``` -->

<!-- ### Validation methods  -->

<!-- ```{r} -->
<!-- #wide data for table -->
<!-- model_validation_wide <- compact_data_with_citation_keys_no_fmd %>%  -->
<!--   count(collab_type, validation, sort = TRUE) %>%  -->
<!--   pivot_wider(names_from = validation, values_from = n) %>%  -->
<!--   replace_na(list(none = 0,  -->
<!--                   data = 0,  -->
<!--                   another_model = 0,  -->
<!--                   none_and_data = 0,  -->
<!--                   data_and_another_model = 0 -->
<!--                   ) -->
<!--              ) %>%  -->
<!--   adorn_totals(where = c('row', 'col')) %>%  -->
<!--   adorn_percentages(... = -c('Total', 'collab_type')) %>%  -->
<!--   adorn_pct_formatting(... = -c('Total', 'collab_type')) %>%  -->
<!--   adorn_ns(... = -c('Total', 'collab_type'))  -->

<!-- #table -->
<!-- knitr::kable(model_validation_wide, caption = 'How the model\'s performance is assessed',  -->
<!--              format = "latex", booktabs = TRUE) %>%  -->
<!--         kableExtra::kable_styling(latex_options = c('striped', 'scale_down', 'HOLD_position')) -->
<!-- ``` -->

>>>>

## Diseases studied per collab type

```{r echo=FALSE}
#count the number of unique diseases studied
disease_studied_by_collab_type <- compact_data_with_citation_keys_no_fmd %>%
  separate_rows(disease,  sep = ' ') %>%
  distinct(title, disease, .keep_all = TRUE) %>%
  count(collab_type, disease, sort = TRUE) %>%
  pivot_wider(names_from = collab_type, values_from = n) %>%
  replace_na(list(purely_academic = 0, mixed = 0)) %>%
  adorn_totals(where = c('row', 'col')) %>%
  adorn_percentages(... = c('purely_academic', 'mixed')) %>%
  adorn_pct_formatting(... = c('purely_academic', 'mixed')) %>%
  adorn_ns(... = c('purely_academic', 'mixed')) %>%
  mutate(disease = str_to_sentence(str_replace(disease, '_', ' '))) %>%
  arrange(desc(Total))

disease_studied_by_collab_type_mod <- rbind(disease_studied_by_collab_type[-1, ], 
                   disease_studied_by_collab_type[1, ])

knitr::kable(disease_studied_by_collab_type_mod, 
             caption = 'Number of studies per disease and collaboration type', 
             format = "latex", booktabs = TRUE) %>%
        kableExtra::kable_styling(latex_options = c('striped', 'HOLD_position'))
```

```{r}
#tally the diseases by collaboration type
disease_by_collab_type_long <- compact_data_with_citation_keys_no_fmd %>%
  separate_rows(disease,  sep = ' ') %>%
  count(collab_type, disease, sort = TRUE)

disease_by_collab_type_plot <- ggplot(disease_by_collab_type_long) +
  geom_bar(aes(x = reorder(disease, n),
               y = n,
               fill = collab_type
               ),
           color = 'black',
           stat = 'identity',
           position = position_fill(reverse = TRUE)
           ) +
  labs(x = 'Disease', y = 'Number of studies') +
  coord_flip() +
  theme_minimal(base_size = 12)

print(disease_by_collab_type_plot)
```

@@

### Parametrization methods

```{r}
#wide data for table
model_parametrization_wide <- compact_data_with_citation_keys_no_fmd %>%
  count(collab_type, parametrization, sort = TRUE) %>%
  pivot_wider(names_from = parametrization, values_from = n) %>%
  adorn_totals(where = c('row', 'col')) %>%
  adorn_percentages(... = -c('Total', 'collab_type')) %>%
  adorn_pct_formatting(... = -c('Total', 'collab_type')) %>%
  adorn_ns(... = -c('Total', 'collab_type'))

#table
knitr::kable(model_parametrization_wide, 
             caption = 'How model parameters are obtained',
             format = "latex", booktabs = TRUE) %>%
        kableExtra::kable_styling(latex_options = c('striped', 
                                                    'scale_down', 
                                                    'HOLD_position')
                                  )
```

### Validation methods

```{r}
#wide data for table
model_validation_wide <- compact_data_with_citation_keys_no_fmd %>%
  count(collab_type, validation, sort = TRUE) %>%
  pivot_wider(names_from = validation, values_from = n) %>%
  replace_na(list(none = 0,
                  data = 0,
                  another_model = 0,
                  none_and_data = 0,
                  data_and_another_model = 0
                  )
             ) %>%
  adorn_totals(where = c('row', 'col')) %>%
  adorn_percentages(... = -c('Total', 'collab_type')) %>%
  adorn_pct_formatting(... = -c('Total', 'collab_type')) %>%
  adorn_ns(... = -c('Total', 'collab_type'))

#table
knitr::kable(model_validation_wide, 
             caption = 'How the model\'s performance is assessed',
             format = "latex", booktabs = TRUE) %>%
        kableExtra::kable_styling(latex_options = c('striped', 
                                                    'scale_down', 
                                                    'HOLD_position')
                                  )
```
